%-------------------------
% Resume in Latex
% Author : Luke Son
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Luke Son} \\ \vspace{1pt}
    \small 619-857-5513 $|$ \href{mailto:lukesson1112@gmail.com}{\underline{lukesson1112@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/luke-son-98a425345/}{\underline{linkedin}} $|$
    \href{https://github.com/asianbike}{\underline{github}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Rutgers University - New Brunswick}{New Brunswick, NJ}
      {Bachelor of Science in Computer Science}{Sep. 2025 -- May 2028}
    \resumeSubheading
      {San Diego State University}{San Diego, CA}
      {Exchange Student}{Jan. 2025 -- May 2025}
    \resumeSubheading
      {Sejong University}{Seoul, South Korea}
      {Bachelor of Science in Computer Engineering}{Mar. 2021 -- Dec 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Social Security Agent}{Dec. 2022 -- Sep 2024}
      {Seoul Metropolitan Fire \& Disaster HQ}{Seoul, South Korea}
      \resumeItemListStart
        \resumeItem{Managed 20+ years of operational and volunteer data, improving reporting accuracy by 25\% and supporting efficient disaster response decision-making; utilized SQL for querying and organizing large datasets.}
        \resumeItem{Assisted in oversaw 300+ computers, resolving 95\% of technical issues using diagnostic tools, ensuring a 99\% uptime for the disaster response network system.}
        \resumeItem{Configured network equipment and secure intranet for a disaster command post during the National drill, enabling 100+ personnel to access critical systems 30\% faster through optimized VLAN setup.}
      \resumeItemListEnd
   
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

     \resumeSubheading
      {Co-Founder \& Digital Experience Lead}{Mar. 2023 -- Dec 2023}
      {Carrierfree}{Seoul, South Korea}
      \resumeItemListStart
        \resumeItem{Conceptualized and developed a web platform for winter jacket rentals, utilizing AWS S3 and EC2 for scalable storage and deployment, catering to Southeast Asian tourists' need for cost-effective, hassle-free travel by using JavaScript, HTML5, CSS, JSON.}
        \resumeItem{Led a cross-functional team of 3 developers, coordinating sprints and code reviews, resulting in the agile delivery of the platform two weeks ahead of schedule.}
        \resumeItem{Implemented a multilingual interface with automatic language detection, enhancing user engagement and attracting 500+ unique visitors in the first two months.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {\textbf{Reddit-style Backend Clone} $|$ \emph{FastAPI, PostgreSQL, SQLAlchemy, Docker}}{June 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed secure REST API for user signup, post creation, and commenting with FastAPI and SQLAlchemy}
            \resumeItem{Designed relational models with Pydantic validation and password hashing using bcrypt  }
            \resumeItem{Integrated PostgreSQL in Docker and structured project with routers/schemas for maintainability}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{AI Resume Analyzer} $|$ \emph{Flask, Groq API, LLaMA3, Bootstrap, Jinja2, Render}}{May 2025 -- June 2025}
          \resumeItemListStart
            \resumeItem{Built a web app that compares PDF resumes and job descriptions using LLaMA3 and DeepSeek via Groq API }
            \resumeItem{Extracted and embedded text from PDFs to compute semantic similarity between resume and job posting content  }
            \resumeItem{Designed UI with Bootstrap and deployed to Render with modular Flask/Jinja2 structure}
          \resumeItemListEnd
        
        \resumeProjectHeading
          {\textbf{Conversion Rate Analysis} $|$ \emph{Python, PyTorch, Google Analytics}}{May 2023 -- June 2023}
          \resumeItemListStart
            \resumeItem{Analyzed 500+ customer interactions, including user behavior and website traffic patterns, to uncover bottlenecks in the conversion funnel.}
            \resumeItem{Designed and implemented machine learning models (Logistic Regression, Random Forest) to predict user conversion likelihood to optimize predictions and validate model performance.}
            \resumeItem{Utilized Python, PyTorch for data preprocessing, feature engineering, and model training, ensuring scalability and reproducibility in a large-scale code project.}
          \resumeItemListEnd
     
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, SQL(PostgreSQL), HTML5, CSS, JSON, C} \\
     \textbf{Frameworks}{: FastAPI, Flask, Bootstrap, Jinja2} \\
     \textbf{Developer Tools}{: Git, GitHub, Docker, AWS (EC2, S3), Azure, Render, Uvicorn} \\
     \textbf{Libraries}{: SQLAlchemy, Pydantic, bcrypt, PyTorch, TensorFlow, Matplotlib, Scikit-learn}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
